Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-08 ii/paper/paper.tex
Text

\begin{figure}[H]
\includegraphics[scale=0.3]{./gfx/pseudocode.png}
\centering
\end{figure}

@@

\subsection{Brute force}

\section{Impact in the scientific community}

\section{Relevance as of 2018}

>>>>

\begin{figure}[h]
\includegraphics[scale=0.4]{./gfx/pseudocode.png}
\centering
\end{figure}

@@

\subsection{Ordering}

$p_j(u)$ be the probability of another page in $D$, which has a flipped bit in position $j$ in the simhash of a page $u$ with $p_j(u) = P(Y_j > |W_j(u)|)$.
$Y$ is the random weight chance that occurs to changes in a document with $Y = X_j^{\alpha} - X_j^{\beta}$, where $X_j^{\alpha} - X_j^{\beta}$ are corresponding to the changed features.

Now it's possible to order and limit the Hamming search to the most likely subsets of hash bits.
For this let $S \subseteq \{1,2,\dots, b\}$ be a subset of non-empty hash bits.
The probability for the existence of a page in $D$ with differing bits on $S$ is then:

\[p(u,S) = \prod_{i \in S}p_i(u) \prod_{j \notin S}(1-p_j(u)) \]

Creating all possible subsets of $S$ in decreasing would be too time and space consuming, since it requires $\Theta(l \log l)$ operations and $\Theta(\sum_{i=1}^{h} ({b \atop i}))$ space.

\subsection{Volatility Heap}
To tackle the computation power and space requirement problems mentioned in the section above, the authors of~\cite{inproc:main} create a new data structure they call \emph{Volatility Ordered Set Heap} (VOSH).

W

\section{Impact in the scientific community}
This paper has been cited by 36 different publications.
Considering this paper has been released 2011, it's still cited by papers and books in 2019, which makes it still valuable contribution to the scientific community.

\section{Relevance as of 2019}
Near duplicate detection is still a very important research field.
The current trend shows, that data will continue to be generated in a exponential manner.

For instance, Google started using \emph{simhash} in 2007 for their web-crawling services~\cite{Manku:2007:DNW:1242572.1242592}.
With Google being one of the biggest Internet companies and the number one search engine, relevance of this topic is obviously very high.
